Turbulence in compact to giant HII regions

### 2022-04-08 strucfunc_paper.tex
Javier changes 2022-04-08

In Appendix~\ref{sec:finite-box-effects} we consider the effects
on the structure function of the finite size \(L\) of the observational map.
If the true correlation length \(r_0\) is more than a small fraction of the map size
(approximately, \(r_0 > 0.1 L\)),
then the apparent velocity variance \(\sigma^2'\) measured directly from the data
is less than the true \(\sigma^2\) of the underlying fluctuations
(see Figure~\ref{fig:finite-box-effect}).
This is because the observed map is not large enough to sample
the full range of velocity variations.
At the same time, the apparent correlation length \(r_0'\) is smaller
than the true value.

@@

%structure functions plots descriptions
Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig. \ref{fig:velocity-maps}. 
In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}), hence the reason that large separation values are not used since they are not consider in our model. 
In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing and the rest would be coincident with the power-law behavior.
The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.

Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B_{\text{noise}}\).
These values were obtained using the LM method.
For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.
%For the discussion of our results in the next paragraphs the small scales would refer to the separations \(r < r_0\) and large scales would refer to separations \(r > r_0\).

@@

The Figure~\ref{fig:strucfunc-fit-M8}a shows the structure function of the Lagoon nebula.
There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
In this case we merge the first two points.
The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
The first maximum value of \(B(r)\) in the order of 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Considering an oscillating behavior at \SI{4.5}{pc} a minimum value of \SI{11}{km^{2}.s^{-2}} is reached.
From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.

@@

In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
The seeing is \SI{0.3}{pc} (\(s_0\)=\SI{0.1}{\arcsecond}) and for this region only the first two points are below the true model. 
The correlation length is \SI{12}{pc} at a \(\sigma^2\pos\) of \SI{54}{km^{2}.s^{-2}} and an index of \num{1.3}.
At large scales the structure function behaves following the tapered fluctuations pattern.
A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
From there the structure functions decays following and inhomogeneous pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.

@@

The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-OrionLH}a.
This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) value of \SI{4}{km^{2}.s^{-2}}.

%corner plots descriptions
Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} right panels show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints. 
These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
They also show the distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.

>>>>

In Appendix~\ref{sec:finite-box-effects} we consider the effects
on the structure function of the finite size \(L\) of the observational map.
If the true correlation length \(r_0\) is more than a small fraction of the map size
(approximately, \(r_0 > 0.1 L\)),
then the apparent velocity variance \(\sigma\pos^2\) measured directly from the data
is less than the true \(\sigma\pos^2\) of the underlying fluctuations
(see Figure~\ref{fig:finite-box-effect}).
This is because the observed map is not large enough to sample
the full range of velocity variations.
At the same time, the apparent correlation length \(r_0'\) is smaller
than the true value.

@@

%structure functions plots descriptions
Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig. \ref{fig:velocity-maps}. 
In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}).
The points left our correspond to the largest separations that are not consider in our model. 
In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing.
The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.

Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B_{\text{noise}}\).
These values were obtained using the LM method.
For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.

@@

The Figure~\ref{fig:strucfunc-fit-M8}a shows the structure function of the Lagoon nebula.
There aren't any points affected by the seeing which has a value of \SI{0.006}{pc} (\(s_0\)=\SI{1}{\arcsecond}).
In this case we merge the first two points.
The Lagoon nebula presents a non-uniform behavior below the correlation length but it is possible to see the characteristic ascending values of the structure function.
The turbulent parameters that fits our model are a \(r_0\) of \SI{1}{pc}, a \(\sigma^2\pos\) of \SI{7}{km^{2}.s^{-2}} and an index of \num{1.17}.
At large scales there is an indication of some periodic behavior followed by ascending \(B(r)\) values at largest separation.
A value of\(B(r)\) of order 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Then there is a diminution at \SI{4.5}{pc} down to a value of \SI{11}{km^{2}.s^{-2}}.
From this point the structure function ascends until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.

@@

In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
The seeing is \SI{0.3}{pc} (\(s_0\)=\SI{0.1}{\arcsecond}) and for this region only the first two points are below the true model. 
The correlation length is \SI{12}{pc} at a \(\sigma^2\pos\) of \SI{54}{km^{2}.s^{-2}} and an index of \num{1.3}.
At large scales the structure function behaves following the tapered fluctuations pattern.
A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
From there the structure functions decays following a scatter pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.

@@

The EON structure function is shown in Figure~\ref{fig:strucfunc-fit-OrionLH}a.
This observations are heavily affected by the noise which presents a value of \SI{6}{km^{2}.s^{-2}} which is larger that the \(\sigma^2\pos\) value of \SI{4}{km^{2}.s^{-2}}. 
%corner plots descriptions
Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} right panels show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints. 
These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
They also show the distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
A number of fits for the equations \ref{eq:sf-functional} and \ref{eq:functional} using samples of the posteriors are shown in thin translucent orange and green lines, respectively, showing the possible range of the confidence intervals.
